new_analses

### 2021-06-10 new_analyses.Rmd
as

```{r}
library(tidyverse)
library(lubridate)
library(drc)
library(broom)
```

@@

```{r}
data3 %>% 
  ggplot(aes(x = dap, y = prob, color = crop)) +
  geom_point() +
  facet_grid(location ~ month)
```

# Arlington

```{r}
arlington <- data3 %>% 
  filter(location == "arlington") %>% 
  filter(month == "July")
```

```{r}
model_arl <- drm(prob*100 ~ doyh, crop, fct = W2.3(), data = arlington)

plot(model_arl, col = c(1,2,3), type = "average", ylab = "Cumulative flowering (%)",
     xlab = "Day of the year")
```

```{r}
#broom::tidy(model_arl)
summary(model_arl)
```

```{r}
ED(model_arl, c(10, 50, 90), interval = "delta", type = "absolute")
```

>>>>

```{r}
library(tidyverse)
library(lubridate)
library(drc)
library(broom)
library(tidytext)
library(ggthemes)
```

@@

```{r}
data3 %>% 
  ggplot(aes(x = dap, y = prob, color = crop)) +
  geom_point() +
  facet_grid(location ~ month)
```
```{r}
car::leveneTest(prob ~ location, data = data3)
```

```{r}
data3 %>% 
  unite("trt", c("location", "crop"), sep = "-") -> data4
```

# June

```{r}
june <-  data4 %>% 
  filter(month == "June")
model <- drm(prob*100 ~ doyh, trt, fct = W2.3(fixed = c(NA, 100, NA)), data = june)

plot(model, col = c(1,2,3), type = "average", ylab = "Cumulative flowering (%)",
     xlab = "Day of the year")
```
```{r}
#broom::tidy(model_arl)
summary(model)
```

```{r}
ed_values <- ED(model, c(10, 50, 90), interval = "delta", type = "absolute")
```

```{r}
ed_values %>% 
  as.data.frame() %>% 
  rownames_to_column(., var = "name") %>% 
  as_tibble() %>% 
  separate(name, c("param", "trt", "ED"), sep = ":") %>% 
  janitor::clean_names() -> ed_values1
```

```{r}
ed_values1 %>% 
  mutate_if(is_character, as_factor) %>% 
  mutate(trt = reorder_within(trt, by = estimate, within = ed)) %>% 
  ggplot(aes(x = trt, y = estimate)) +
  scale_x_reordered() +
  geom_point() +
  geom_linerange(aes(ymin = lower, ymax = upper)) +
  labs(y = NULL, x = NULL,
       title = "DOY of 10, 50, and 90% Palmer amaranth flowering") +
  coord_flip() +
#  scale_color_brewer(palette = "Paired") +
  facet_wrap(~ ed, scales = "free") +
  theme_bw() +
  theme(legend.position = "none") +
  ggsave("june.png", width = 12, height = 5)
```

# July

```{r}
july <-  data4 %>% 
  filter(month == "July")
model1 <- drm(prob*100 ~ doyh, trt, fct = W2.3(fixed = c(NA, 100, NA)), data = july)

plot(model1, col = c(1,2,3), type = "average", ylab = "Cumulative flowering (%)",
     xlab = "Day of the year")
```

```{r}
#broom::tidy(model_arl)
summary(model1)
```

```{r}
ed_values <- ED(model1, c(10, 50, 90), interval = "delta", type = "absolute")
```
